### 2017-03-09 cv-body.tex
Tweak CV
Update CV
CV

\begin{description}
\tightlist
\item[2015--16]
David H. Smith Conservation Research Fellow, School of Aquatic and
Fishery Sciences, University of Washington and Northwest Fisheries
Science Center, Seattle, USA
\item[2015]
Post-doctoral Fellow, School of Resource and Environmental Management,
Simon Fraser University, Burnaby, Canada
\item[2011--15]
Graduate Research Assistant, Department of Biological Sciences, Simon
Fraser University, Burnaby, Canada
\item[2008--11]
Graduate Research Assistant, Department of Biology, Dalhousie
University, Halifax, Canada
\end{description}

@@

@@

and Fisheries. In press.

>>>>

\begin{description}
\tightlist
\item[2015--17]
David H. Smith Conservation Research Fellow, School of Aquatic and
Fishery Sciences, University of Washington and Northwest Fisheries
Science Center, Seattle, USA
\item[2015]
Postdoctoral Fellow, School of Resource and Environmental Management,
Simon Fraser University, Burnaby, Canada
\item[2011--15]
Graduate Research Assistant, Department of Biological Sciences, Simon
Fraser University, Burnaby, Canada
\item[2008--11]
Graduate Research Assistant, Department of Biology, Dalhousie
University, Halifax, Canada
\end{description}

@@

\item[2017]
\textbf{Anderson, S.C.}, T.A. Branch, A.B. Cooper, N.K. Dulvy.
Black-swan events in animal populations. Proceedings of the National
Academy of Sciences. In press.
\url{http://doi.org/10.1073/pnas.1611525114} (Open access).
\item[2017]

@@

and Fisheries. In press. \url{http://doi.org/10.1111/faf.12200}.
